Analysis of Tick-Bourne Disease Cases Reported to DPH Between 2019-2024

### 2025-03-13 products/manuscript/Manuscript.qmd
Fixed rendering error
Found an error that I made after initial render check in omitting a .png that made it so the manuscript could not find the file that I created in the processing code

# Generate correct file paths
img_paths <- c(
  here::here("results", "figures", "disease_county_plot.png"),
  here::here("results", "figures", "top5_disease_county_plot.png")
)

>>>>

# Generate correct file paths
img_paths <- c(
  here::here("results", "figures", "disease_county_plot.png"),
  here::here("results", "figures", "top5_diseases_stacked_plot.png"),
  here::here("results", "figures", "top5_disease_county_plot.png")
)
